Objectification Special Studies Analysis

### 2019-03-26 full analysis file.Rmd
Fixed paths

Load data
```{r}
#clark
clark_measures <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

#sentence data
#clark_sentence_long1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long.sav")

#clark_sentence_wide1 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide.sav")

#clark_sentences_long2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_long2.sav")

#clark_sentence_wide2 <- read_spss("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/sentences_wide2.sav")

clark_sentences <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

smith_trigrams_graded <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_graded.csv")

@@

#coding correlations
kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_sentences_coded.csv")

xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_sentences.csv")

@@

##TAKE TWOOOO
kat_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")

xinyu_codes2 <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")

>>>>

Load data
```{r}
#clark
clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

#sentence data

clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")

@@

#coding correlations
kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_sentences_coded.csv")

xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_sentences.csv")

@@

##TAKE TWOOOO
kat_codes2 <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")

xinyu_codes2 <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")
